---
title: "Final Project_Amin"
output: 
  flexdashboard::flex_dashboard:
    theme: cosmo
    source: embed
    smart: false
runtime: shiny
---

```{r include = FALSE}

# LOAD PACKAGES

library(DT)
library(ggmap)
library(shiny)
library(knitr)
library(pander)
library(leaflet)
library(viridis)
library(rsconnect)
library(tidyverse)
library(flexdashboard)
library(prettydoc)



# READ IN DATA

url <- paste0("https://github.com/DS4PS/Data-",
              "Science-Class/blob/master/DATA",
              "/TempeTrafficAccidents.rds?raw=true")

dat <- readRDS(gzcon(url(url)))



# DATA PREPROCESSING I: INJURIES & FATALITIES

dat        <- na.omit(dat)                                       # Remove NAs
dat$fatal  <- dat$Totalfatalities > 0                            # 1+ fatalities
dat$inj    <- dat$Totalinjuries > 0 & dat$Totalfatalities == 0   # 1+ injury, 0 fatal
dat$nohurt <- dat$Totalfatalities + dat$Totalinjuries == 0       # Harmless

date.vec   <- strptime(dat$DateTime, format = "%m/%d/%y %H:%M")  # Datetime variables
dat$hour   <- format(date.vec, format = "%H") %>% as.numeric()
dat$month  <- format(date.vec, format = "%b")
dat$day    <- format(date.vec, format = "%a")
dat$day365 <- format(date.vec, format = "%j")
dat$week   <- format(date.vec, format = "%V")



# DATA PREPROCESSING II: NAMED INTERVALS OF TIME

dat <- dat %>% 
  mutate(time.of.day = case_when(hour >= 6 & hour <= 9 ~ "Morning Commute", 
                                 hour >= 16 & hour <= 19 ~ "Evening Commute", 
                                 hour >= 14 & hour <= 15 ~ "School Pickup", 
                                 hour >= 9 & hour <= 13 ~ "Work", 
                                 hour >= 20 & hour <= 23 ~ "Night", 
                                 hour <= 5 & hour >= 0 ~ "Midnight to Dawn"))

dat$harm <- ifelse( dat$Totalinjuries > 0 | dat$Totalfatalities > 0, "Harm", "No Harm" )



# DATA PREPROCESSING III: PERMUTATIONS OF INEBRIATION

dat <- dat %>% 
  mutate(d1.substance = case_when(AlcoholUse_Drv1 == "Alcohol" & 
                                  DrugUse_Drv1 == "No Apparent Influence" ~ "Alcohol", 
                                  AlcoholUse_Drv1 == "No Apparent Influence" & 
                                  DrugUse_Drv1 == "Drugs" ~ "Drugs", 
                                  AlcoholUse_Drv1 == "Alcohol" & 
                                  DrugUse_Drv1 == "Drugs" ~ "Alcohol and Drugs", 
                                  AlcoholUse_Drv1 == "No Apparent Influence" & 
                                  DrugUse_Drv1 == "No Apparent Influence" ~ "No Apparent
                                  Influence"))

dat <- dat %>% 
  mutate( d2.substance = case_when(AlcoholUse_Drv2 == "Alcohol" & 
                                   DrugUse_Drv2 == "No Apparent Influence" ~ "Alcohol", 
                                   AlcoholUse_Drv2 == "No Apparent Influence" & 
                                   DrugUse_Drv2 == "Drugs" ~ "Drugs", 
                                   AlcoholUse_Drv2 == "Alcohol" & 
                                   DrugUse_Drv2 == "Drugs" ~ "Alcohol and Drugs", 
                                   AlcoholUse_Drv2 == "No Apparent Influence" & 
                                   DrugUse_Drv2 == "No Apparent Influence" ~ "No Apparent
                                   Influence"))



# DATA PREPROCESSING IV: AGE CATEGORIES

dat$age.cat <- case_when(dat$Age_Drv1 >= 0 & 
                         dat$Age_Drv1 <= 18 ~ "Youth", 
                         dat$Age_Drv1 >= 19 & 
                         dat$Age_Drv1 <= 25 ~ "Young Adult", 
                         dat$Age_Drv1 >= 26 & 
                         dat$Age_Drv1 <= 64 ~ "Adult", 
                         dat$Age_Drv1 >= 65 ~ "Senior")

                        
```

# Traffic Accidents By Day and Time

## Inputs {.sidebar}

```{r}
checkboxGroupInput("days", label = h3("Day of Week"), 
    choices = list("Monday"    = "Mon", 
                   "Tuesday"   = "Tue", 
                   "Wednesday" = "Wed", 
                   "Thursday"  = "Thu",
                   "Friday"    = "Fri",
                   "Saturday"  = "Sat",
                   "Sunday"    = "Sun" ),
    selected = c("Fri","Sat","Sun"))

sliderInput("hour", label = h3("Time of Day"), 
            min = 0, max = 23, value = c(6, 12))

# parameters

```

## Outputs

### Traffic Accidents By Day and Time

```{r}

# LEAFLET MAPPING

renderLeaflet({
  
  days.of.week <- input$days    # Vector of checked days
  start.time <- input$hour[1]   # Slider input of lower time range
  end.time  <-  input$hour[2]   # Slider input of upper time range
  
  d2 <- dat %>%
    filter(day %in% input$days, 
           hour >= start.time & hour <= end.time)
  
  d2$col.vec <- ifelse( d2$nohurt, "gray20", 
                        ifelse(d2$inj, "steelblue", "darkorange") ) 
  
  point.size <- d2$Totalinjuries + d2$Totalfatalities

  crash.details <- paste0("Time: ", d2$DateTime, "<br>",
                          "Total Fatalities: ", d2$Totalfatalities, "<br>",
                          "Total Injuries: ", d2$Totalinjuries, "<br>",
                          "Collision type: ", d2$Collisionmanner)
  
  tempe <- leaflet( ) %>% 
    addProviderTiles("CartoDB.Positron")  %>%
    setView(lng = -111.9278, 
            lat = 33.39951, 
            zoom = 13)
  
  
  addCircles(tempe, 
             lng = d2$Longitude, 
             lat = d2$Latitude,
             fillColor = d2$col.vec, 
             fillOpacity = 0.5, 
             stroke = FALSE, 
             radius = 50*(1+0.33*point.size),
             popup = crash.details)


})

```

# Collision Type by Ambient Condition

## Inputs {.sidebar}

```{r}



selectInput(inputId = "colli.type", 
                   label = h3("Collision Vissued for Driver 1"), 
    choices =  c("Rear End", 
                 "Left Turn", 
                 "Head On",
                 "Sideswipe Same Direction"),
                 
    
            selected = "Rear End")

selectInput(inputId = "light.type", 
                   label = h3("Lighting Condition"), 
    choices =  c("Daylight", 
                 "Dusk", 
                 "Dark Lighted"),
    
            selected = "Daylight")


radioButtons(inputId = "d1.age.group", 
             label = h4("Driver 1 Age Group"),
             choices = c("Youth", 
                         "Young Adult", 
                         "Adult", 
                         "Senior"),
             selected = c("Youth") )



radioButtons(inputId = "weather.type", 
             label = h4("Weather Condition"),
             choices = c("Blowing Sand Soil Dirt", 
                         "Clear", 
                         "Cloudy"), 
                      
             selected = c("Clear") )



# parameters

```

## Outputs

### Collision Type by Ambient Condition

```{r}

# LEAFLET MAPPING

renderLeaflet({
  
  Collition_type <- input$colli.type 
  Lighting_type <- input$light.type
  Weather_type <- input$weather.type
  D1_age <- input$d1.age.group
  
  
  d2 <- dat %>%
    filter(
           Collisionmanner %in% Collition_type, 
           Lightcondition %in% Lighting_type,
           Weather %in% Weather_type ,
           age.cat %in% D1_age,
         
           )
           
          
  
  d2$col.vec <- ifelse( d2$nohurt, "gray20", 
                        ifelse(d2$inj, "steelblue", "darkorange") ) 
  
  point.size <- d2$Totalinjuries + d2$Totalfatalities

  crash.details <- paste0("Time: ", d2$DateTime, "<br>",
                          "Total Fatalities: ", d2$Totalfatalities, "<br>",
                          "Total Injuries: ", d2$Totalinjuries, "<br>",
                          "Collision type: ", d2$Collisionmanner)
  
  tempe <- leaflet( ) %>% 
    addProviderTiles("CartoDB.Positron")  %>%
    setView(lng = -111.9278, 
            lat = 33.39951, 
            zoom = 13)
  
  
  addCircles(tempe, 
             lng = d2$Longitude, 
             lat = d2$Latitude,
             fillColor = d2$col.vec, 
             fillOpacity = 0.5, 
             stroke = FALSE, 
             radius = 50*(1+0.33*point.size),
             popup = crash.details)


})

```

# Violations issued by conditions

## Inputs {.sidebar}

```{r}


selectInput(inputId = "violation.d1", 
                   label = h3("Violation for driver1"), 
    choices =  c("Inattention Distraction",
                 "Speed To Fast For Conditions",
                 "Made Improper Turn",
                 "Unknown",
                 "Failed To Keep In Proper Lane",
                 "Disregarded Traffic Signal",
                 "Other",
                 "Failed To Yield Right Of Way",
                 "Exceeded Lawful Speed ",
                 "Electronic Communications Device"),
                selected = "Speed To Fast For Conditions")

checkboxGroupInput(inputId = "substance.d1", 
            label = h4("Driver 1 Substance"), 
            choices = c("Alcohol", 
                        "Drugs", 
                        "No Apparent Influence", 
                        "Alcohol and Drugs"),
            selected = c("Alchohol" , "Drugs"))

  

radioButtons(inputId = "time.of.day", 
             label = h4("Time of Day"),
             choices = c("Morning Commute", 
                         "Evening Commute", 
                         "School Pickup", 
                         "Work", 
                         "Night", 
                         "Midnight to Dawn"),
             selected = c("Morning Commute") )

checkboxGroupInput(inputId = "gender", 
             label = h4("gender of driver1"),
             choices = c("Male",
                         "Unknown",
                         "Female") ,
                         
             selected = c("Male") )



# parameters
```

## Outputs

### Violations issued by conditions

```{r}

# LEAFLET MAPPING

renderLeaflet({
  
  Violation_issued_d1 <- input$violation.d1
  Substance_driver1 <- input$substance.d1
  Time_of_day <- input$time.of.day
  Gender_d1 <- input$gender
  
  
  d2 <- dat %>%
    filter(
           Violation1_Drv1 %in% Violation_issued_d1,
           d1.substance %in% Substance_driver1,
           time.of.day %in% Time_of_day,
           Gender_Drv1 %in% Gender_d1
           )
           
          
  
  d2$col.vec <- ifelse( d2$nohurt, "gray20", 
                        ifelse(d2$inj, "steelblue", "darkorange") ) 
  
  point.size <- d2$Totalinjuries + d2$Totalfatalities

  crash.details <- paste0("Time: ", d2$DateTime, "<br>",
                          "Total Fatalities: ", d2$Totalfatalities, "<br>",
                          "Total Injuries: ", d2$Totalinjuries, "<br>",
                          "Collision type: ", d2$Collisionmanner)
  
  tempe <- leaflet( ) %>% 
    addProviderTiles("CartoDB.Positron")  %>%
    setView(lng = -111.9278, 
            lat = 33.39951, 
            zoom = 13)
  
  
  addCircles(tempe, 
             lng = d2$Longitude, 
             lat = d2$Latitude,
             fillColor = d2$col.vec, 
             fillOpacity = 0.5, 
             stroke = FALSE, 
             radius = 50*(1+0.33*point.size),
             popup = crash.details)


})

```

# Injuryseverity by travel direction

## Inputs {.sidebar}

```{r}
 #dat$Traveldirection_One



checkboxGroupInput(inputId = "direction", 
                   label = h3("Driver Direction 1"), 
                   choices =  c("North" , "South" , "East" , "West"),
                  selected = "North")

selectInput(inputId = "total.severity", 
            label = h4 ("Injury Severity"),
            choices = c ("No Injury" , 
                         "Possible Injury",
                         "Fatal",
                         "Non Incapacitating Injury",
                         "Incapacitating Injury"),
            selected = "Fatal")
            

# parameters

```

## Outputs

### Injuryseverity by travel direction

```{r}

# LEAFLET MAPPING

renderLeaflet({
  
  driver_direction <- input$direction    
  injury <- input$total.severity
  
  d2 <- dat %>%
    filter(Traveldirection_One %in% driver_direction, 
           Injuryseverity %in% injury)
  
  d2$col.vec <- ifelse( d2$nohurt, "gray20", 
                        ifelse(d2$inj, "steelblue", "darkorange") ) 
  
  point.size <- d2$Totalinjuries + d2$Totalfatalities

  crash.details <- paste0("Time: ", d2$DateTime, "<br>",
                          "Total Fatalities: ", d2$Totalfatalities, "<br>",
                          "Total Injuries: ", d2$Totalinjuries, "<br>",
                          "Collision type: ", d2$Collisionmanner)
  
  tempe <- leaflet( ) %>% 
    addProviderTiles("CartoDB.Positron")  %>%
    setView(lng = -111.9278, 
            lat = 33.39951, 
            zoom = 13)
  
  
  addCircles(tempe, 
             lng = d2$Longitude, 
             lat = d2$Latitude,
             fillColor = d2$col.vec, 
             fillOpacity = 0.5, 
             stroke = FALSE, 
             radius = 50*(1+0.33*point.size),
             popup = crash.details)


})

```

# Driver Characteristics {data-orientation="rows"}

## Sidebar {.sidebar}

Driver Characteristics

```{r}

sliderInput(inputId = "d1age", 
            label = h4("Driver 1 Age"), 
            min = 15, 
            max = 100, 
            value = c(18,36) )

sliderInput(inputId = "d2age", 
            label = h4("Driver 2 Age"), 
            min = 15, 
            max = 100, 
            value = c(18,36) )

selectInput(inputId = "d1gender", 
            label = h4("Driver 1 Gender"), 
            choices = c("Male","Female", "Unknown"), 
            selected = c("Male"))

selectInput(inputId = "d2gender", 
            label = h4("Driver 2 Gender"), 
            choices = c("Male","Female", "Unknown"), 
            selected = c("Male"))

radioButtons(inputId = "d1pedcy", 
             label = h4("Driver 1 Transportation"),
             choices = c("Driver", "Pedalcyclist", "Pedestrian"), 
             selected = c("Driver"))

radioButtons(inputId = "d2pedcy", 
             label = h4("Driver 2 Transportation"),
             choices = c("Driver", "Pedalcyclist", "Pedestrian"), 
             selected = c("Driver"))

```

## Row

### Number of Crashes

```{r}

renderValueBox({
  
  d2 <- dat %>%
    filter(Age_Drv1 >= input$d1age[1] & Age_Drv1 <= input$d1age[2], 
           Age_Drv2 >= input$d2age[1] & Age_Drv2 <= input$d2age[2], 
           Gender_Drv1 %in% input$d1gender, 
           Gender_Drv2 %in% input$d2gender, 
           Unittype_One %in% input$d1pedcy, 
           Unittype_Two %in% input$d2pedcy )
  
  crashes <- count( d2 )
  
  valueBox(crashes, 
           icon = "fa-pencil",
           color = ifelse( crashes > 50, "danger", "primary") )
  
})

```

### Total Injuries

```{r}

renderValueBox({
  
  d2 <- dat %>%
    filter(Age_Drv1 >= input$d1age[1] & Age_Drv1 <= input$d1age[2], 
           Age_Drv2 >= input$d2age[1] & Age_Drv2 <= input$d2age[2], 
           Gender_Drv1 %in% input$d1gender, 
           Gender_Drv2 %in% input$d2gender, 
           Unittype_One %in% input$d1pedcy, 
           Unittype_Two %in% input$d2pedcy)
  
  total.injuries <- sum(d2$Totalinjuries)
  
  valueBox(total.injuries, 
           icon = "fa-angry",
           color = ifelse(total.injuries > 30, "danger", "primary" ))

  })

```

### Total Fatalities

```{r}

renderValueBox({
  
  d2 <- dat %>%
    filter(Age_Drv1 >= input$d1age[1] & Age_Drv1 <= input$d1age[2], 
           Age_Drv2 >= input$d2age[1] & Age_Drv2 <= input$d2age[2], 
           Gender_Drv1 %in% input$d1gender, 
           Gender_Drv2 %in% input$d2gender, 
           Unittype_One %in% input$d1pedcy, 
           Unittype_Two %in% input$d2pedcy)

  total.fatalities <- sum(d2$Totalfatalities)
  
  valueBox(total.fatalities, 
           icon = "fa-briefcase-medical",
           color = ifelse(total.fatalities > 10, "danger", "primary"))
  
})

```

### Rate of Harm

```{r}

renderValueBox({
  
  d2 <- dat %>%
    filter(Age_Drv1 >= input$d1age[1] & Age_Drv1 <= input$d1age[2], 
           Age_Drv2 >= input$d2age[1] & Age_Drv2 <= input$d2age[2], 
           Gender_Drv1 %in% input$d1gender, 
           Gender_Drv2 %in% input$d2gender, 
           Unittype_One %in% input$d1pedcy, 
           Unittype_Two %in% input$d2pedcy)
  
  rate.of.harm <- round(length(which(d2$harm == "Harm"))/count(d2), 3)
  
  valueBox(rate.of.harm, 
           icon = "fa-pencil",
           color = ifelse(rate.of.harm > 0.5, "danger", "primary"))
  
})

```

## Outputs

### Traffic Accidents by Driver Characteristics

```{r}

renderLeaflet({
  
  # days.of.week <- input$days    # vector will all checked values
  # start.time <- input$hour[1]   # sliderInput lower value
  # end.time  <-  input$hour[2] 
  
  d2 <- dat %>%
    filter(Age_Drv1 >= input$d1age[1] & Age_Drv1 <= input$d1age[2], 
           Age_Drv2 >= input$d2age[1] & Age_Drv2 <= input$d2age[2], 
           Gender_Drv1 %in% input$d1gender, 
           Gender_Drv2 %in% input$d2gender, 
           Unittype_One %in% input$d1pedcy, 
           Unittype_Two %in% input$d2pedcy)
  
  d2$col.vec <- ifelse(d2$nohurt, "gray20", 
                       ifelse(d2$inj, "steelblue", "darkorange") )              
    
  point.size <- d2$Totalinjuries + d2$Totalfatalities

  crash.details <- paste0("Time: ", d2$DateTime, "<br>",
                          "Total Fatalities: ", d2$Totalfatalities, "<br>",
                          "Total Injuries: ", d2$Totalinjuries, "<br>",
                          "Collision type: ", d2$Collisionmanner)
  
  tempe <- leaflet() %>% 
    addProviderTiles( "CartoDB.Positron" )  %>%
    setView( lng=-111.9278, lat=33.39951, zoom=13 )
  
  
  addCircles(tempe, lng=d2$Longitude, lat=d2$Latitude,
             fillColor=d2$col.vec, fillOpacity=0.5, 
             stroke=F, radius=50*(1+0.33*point.size),
             popup=crash.details )


})

```

# Comparisons {data-orientation="rows"}

## Sidebar {.sidebar}

Driver Characteristics

```{r}

sliderInput(inputId = "driver.1.age", 
            label = h4("Driver 1 Age"), 
            min = 15, 
            max = 100, 
            value = c(18,36))

sliderInput(inputId = "driver.2.age", 
            label = h4("Driver 2 Age"), 
            min = 15, 
            max = 100, 
            value = c(18,36))

selectInput(inputId = "driver.1.gender", 
            label = h4("Driver 1 Gender"), 
            choices = c("Male","Female", "Unknown"), 
            selected = c("Male"))

selectInput(inputId = "driver.2.gender", 
            label = h4("Driver 2 Gender"), 
            choices = c("Male","Female", "Unknown"), 
            selected = c("Male"))

radioButtons(inputId = "driver.1.pedcy", 
             label = h4("Driver 1 Transportation"),
             choices = c("Driver", "Pedalcyclist", "Pedestrian"), 
             selected = c("Driver"))

radioButtons(inputId = "driver.2.pedcy", 
             label = h4("Driver 2 Transportation"),
             choices = c("Driver", "Pedalcyclist", "Pedestrian"), 
             selected = c("Driver"))

```

## Row

### Number of Crashes

```{r}

renderValueBox({
  
  d2 <- dat %>%
    filter(Age_Drv1 >= input$d1age[1] & Age_Drv1 <= input$d1age[2], 
           Age_Drv2 >= input$d2age[1] & Age_Drv2 <= input$d2age[2], 
           Gender_Drv1 %in% input$d1gender, 
           Gender_Drv2 %in% input$d2gender, 
           Unittype_One %in% input$d1pedcy, 
           Unittype_Two %in% input$d2pedcy )
  
  crashes <- count( d2 )
  
  valueBox(crashes, 
           icon = "fa-pencil",
           color = ifelse( crashes > 50, "danger", "primary") )
  
})

```

### Total Injuries

```{r}

renderValueBox({
  
  d2 <- dat %>%
    filter(Age_Drv1 >= input$d1age[1] & Age_Drv1 <= input$d1age[2], 
           Age_Drv2 >= input$d2age[1] & Age_Drv2 <= input$d2age[2], 
           Gender_Drv1 %in% input$d1gender, 
           Gender_Drv2 %in% input$d2gender, 
           Unittype_One %in% input$d1pedcy, 
           Unittype_Two %in% input$d2pedcy)
  
  total.injuries <- sum(d2$Totalinjuries)
  
  valueBox(total.injuries, 
           icon = "fa-angry",
           color = ifelse(total.injuries > 30, "danger", "primary"))
  
})

```

### Total Fatalities

```{r}

renderValueBox({
  
  d2 <- dat %>%
    filter(Age_Drv1 >= input$d1age[1] & Age_Drv1 <= input$d1age[2], 
           Age_Drv2 >= input$d2age[1] & Age_Drv2 <= input$d2age[2], 
           Gender_Drv1 %in% input$d1gender, 
           Gender_Drv2 %in% input$d2gender, 
           Unittype_One %in% input$d1pedcy, 
           Unittype_Two %in% input$d2pedcy)

  total.fatalities <- sum(d2$Totalfatalities)
  
  valueBox(total.fatalities, 
           icon = "fa-briefcase-medical",
           color = ifelse(total.fatalities > 10, "danger", "primary"))
  
})

```

### Rate of Harm

```{r}

renderValueBox({
  
  d2 <- dat %>%
    filter(Age_Drv1 >= input$d1age[1] & Age_Drv1 <= input$d1age[2], 
           Age_Drv2 >= input$d2age[1] & Age_Drv2 <= input$d2age[2], 
           Gender_Drv1 %in% input$d1gender, 
           Gender_Drv2 %in% input$d2gender, 
           Unittype_One %in% input$d1pedcy, 
           Unittype_Two %in% input$d2pedcy)
  
  rate.of.harm <- round(length(which(d2$harm == "Harm"))/count(d2), 3)
  
  valueBox(rate.of.harm, 
           icon = "fa-pencil",
           color = ifelse(rate.of.harm > 0.5, "danger", "primary"))
  
})

```

## Column

### Driver 1

```{r}

renderLeaflet({
  
  # days.of.week <- input$days    # vector will all checked values
  # start.time <- input$hour[1]   # sliderInput lower value
  # end.time  <-  input$hour[2] 
  
  d10 <- dat %>%
    filter(Age_Drv1 >= input$driver.1.age[1] & Age_Drv1 <= input$driver.1.age[2], 
           Gender_Drv1 %in% input$driver.1.gender, 
           Unittype_One %in% input$driver.1.pedcy )
  
  d10$col.vec <- ifelse(d10$nohurt, "gray20", 
                        ifelse(d10$inj, "steelblue", "darkorange") )              
    
  point.size <- d10$Totalinjuries + d10$Totalfatalities

  crash.details <- paste0("Time: ", d10$DateTime, "<br>",
                          "Total Fatalities: ", d10$Totalfatalities, "<br>",
                          "Total Injuries: ", d10$Totalinjuries, "<br>",
                          "Collision type: ", d10$Collisionmanner)
  
  tempe <- leaflet() %>% 
    addProviderTiles("CartoDB.Positron") %>%
    setView(lng = -111.9278, 
            lat = 33.39951, 
            zoom = 13)
  
  addCircles(tempe, 
             lng = d10$Longitude, 
             lat = d10$Latitude,
             fillColor = d10$col.vec, 
             fillOpacity = 0.5, 
             stroke = F, 
             radius = 50*(1 + 0.33 * point.size),
             popup = crash.details)


})
```

### Driver 2

```{r}

renderLeaflet({
  
  # days.of.week <- input$days    # vector will all checked values
  # start.time <- input$hour[1]   # sliderInput lower value
  # end.time  <-  input$hour[2] 
  
  d11 <- dat %>%
    filter(Age_Drv2 >= input$driver.2.age[1] & Age_Drv2 <= input$driver.2.age[2], 
           Gender_Drv2 %in% input$driver.2.gender, 
           Unittype_Two %in% input$driver.2.pedcy)
  
  d11$col.vec <- ifelse(d11$nohurt, "gray20", 
                        ifelse(d11$inj, "steelblue", "darkorange"))
  
  point.size2 <- d11$Totalinjuries + d11$Totalfatalities

  crash.details2 <- paste0("Time: ", d11$DateTime, "<br>",
                           "Total Fatalities: ", d11$Totalfatalities, "<br>",
                           "Total Injuries: ", d11$Totalinjuries, "<br>",
                           "Collision type: ", d11$Collisionmanner)
  
  tempe2 <- leaflet() %>% 
    addProviderTiles("CartoDB.Positron") %>%
    setView(lng = -111.9278, 
            lat = 33.39951, 
            zoom = 13)
  
  addCircles(tempe2, 
             lng = d11$Longitude, 
             lat = d11$Latitude,
             fillColor = d11$col.vec, 
             fillOpacity = 0.5, 
             stroke = F, 
             radius = 50 * (1 + 0.33 * point.size2),
             popup = crash.details2 )

})

```

# About

## Row

### About this Dashboard

This Dashboard is the final project for Coding in R course. It was created using the [City of Temp Open Data Portal](https://data.tempe.gov/). This dashboard has been built with the intention of analyzing the "crash data" of the city of Tempe. The foundation of this dashboard was created by Dr.Jesse Lecy. This data set contains the locations, the reasons, the time, the age group that got injured. This dashboard can be a good source for filtering data to see the impact of different variables have for each of the crash.

### Dashboard Author

I am **Maisunath Maliha**, currently a masters student in Urban Institute at Georgia State University. My research interest focuses on data analysis as I am policy student. I believe, learning R language can be a valuable skill for policy analysts who want to work with large datasets, conduct statistical analyses, and communicate their findings effectively to policymakers and stakeholders.I have attached my profile through linkedin below.

[Connect via LinkedIn](https://www.linkedin.com/in/maisunath-maliha-amin-114955a1/)

## Row

DATA DICTIONARY

```{r}

url.dd <- paste0("https://raw.githubusercontent.com",
                 "/DS4PS/cpp-526-fall-2019/master/l",
                 "abs/final-project/TempeTrafficAcc",
                 "identsDataDictionary.csv")

data.dictionary <- read.csv(url.dd, 
                            stringsAsFactors = FALSE)

data.dictionary$description <- stringi::stri_trans_general(data.dictionary$description,
                                                           "latin-ascii")

data.dictionary %>%
  select(column, description) %>%
  pander()

```

# Data

```{r}

# library( DT )

these.buttons <- c('copy', 'csv', 'pdf', 'print')

renderDataTable({
  
  datatable(dat[1:100, ], 
            filter = 'bottom', 
            rownames = FALSE, 
           #options=list( pageLength=5, autoWidth=TRUE ),
            fillContainer = TRUE, 
            style = "bootstrap",
            class = 'table-condensed table-striped',
            extensions = 'Buttons', 
            options = list(dom = 'Bfrtip', 
                           buttons=these.buttons))

  })

```
